---
title: "Simulation 3_1"
author: "Jeremy J Lin"
date: "`r Sys.Date()`"
output: 
  pdf_document :
    keep_tex: true
    extra_dependencies: "subfig"
header-includes:
 - \usepackage{booktabs}
 - \usepackage{longtable}
 - \usepackage{array}
 - \usepackage{multirow}
 - \usepackage{wrapfig}
 - \usepackage{float}
 - \usepackage{subfig}
 - \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nlme)
library(Matrix)
library(MASS)
library(rootSolve)
library(geepack)
library(lme4)
library(mvtnorm)
library(reshape2)
library(knitr)
library(ggplot2)
library(tidyr)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(kableExtra)
library(corrplot)
library(robustHD)
library(pracma)
library(xtable)
library(latex2exp)
library(janitor)
library(ggpubr)
# parallel computing libraries
library(foreach)
#library(doMC)
# beep beep 
library(beepr)
library(doParallel)
library(doSNOW)
library(utils)
library(foreach)
library(doRNG)
library(geepack)
```

```{r echo=FALSE}
#rm(list = ls())

knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, results = "hide", 
                      fig.pos = 'H', cache = FALSE, 
                      eval = FALSE)
# load functions
source("~/Documents/Research/LMM_Project/dgm simutlations/R_functions.R")
```

<!-- Functions -->

# Simulation Settings 

Repeated across 400 simulations with different combination of small total T and small total n.
We would like to compare this with the theoretical asymptotic variance with sample size adjustment

Availability depends on time, with linear treatment effect 

\begin{align*}
  Y_{i, t, 1} | H_t, A_t &= I_{(A_{i,t} = 1)} \beta_1 + I_{(A_{i,t} = 2)} \beta_2 + 1 + \epsilon_{i,t}\\
  A_{i,t} &= \{0, 1, 2\}\\
  P(A_t = 0 |H_t) &=\tilde{p_0}  = 0.2\\
  P(A_t = 1 |H_t) &=\tilde{p_1}  = 0.5\\
  P(A_t = 2 |H_t) &=\tilde{p_2}  = 0.3\\
  P(I_t = 0.5)\\
  \beta_1 &= 0.1\\
  \beta_2 &= 0.4
\end{align*}

```{r}
# change font size, legend position
myggfont <- function(legend_pos = NULL,
                     legend_text_size = 18,
                     legend_title_size = 20,
                     axis_text_size = 16,
                     axis_title_size = 20,
                     plot_title_size = 20,
                     facet_text_size = 16) {
  ff <- theme(legend.text = element_text(size = legend_text_size),
              legend.title = element_text(size = legend_title_size),
              axis.text = element_text(size = axis_text_size),
              axis.title = element_text(size = axis_title_size, face="bold"),
              plot.title = element_text(size = plot_title_size),
              strip.text.x = element_text(size = facet_text_size),
              strip.text.y = element_text(size = facet_text_size))
  if (is.null(legend_pos)) {
    return(ff)
  } else if (legend_pos == "top-left") {
    return(ff + theme(legend.justification = c(0,1), legend.position = c(0,1)))
  } else if (legend_pos == "top-right") {
    return(ff + theme(legend.justification = c(1,1), legend.position = c(1,1)))
  } else if (legend_pos == "bottom-left") {
    return(ff + theme(legend.justification = c(0,0), legend.position = c(0,0)))
  } else if (legend_pos == "bottom-right") {
    return(ff + theme(legend.justification = c(1,0), legend.position = c(1,0)))
  } else {
    stop("legend_pos needs to be NULL, top-left, top-right, bottom-left, or bottom-right.")
  }
}
```


```{r}
source("~/Documents/Research/causal_excursion_mult_trt/simulation_results/Power Simulation/viol_2/sim_4_2a/functions_util.R")
# read simulation design 
SD <- readRDS("~/Documents/Research/causal_excursion_mult_trt/simulation_results/Power Simulation/viol_2/sim_4_2a/Simulation_design.RDS")
n_seed = 5 
nsim = 500
truth_hypothesis = "H1"
dim(SD)

result_list = list()
for (isim in 1:n_seed) {
  fileName = paste("results_sim_4_2a_setting_",isim,"_",nsim,".RDS",sep = "")
  res <- readRDS(paste0(fileName))
  print(length(res))
  result_list <- c(result_list, res)
}
length(result_list)

setting = length(result_list)
result_df_collected <- data.frame()
result_list_collected <- list()

start_time <- Sys.time()

for (isetting in 1:setting) {
  
  current_time <- Sys.time()
  print(Sys.time())
  print(paste0(round(difftime(current_time, start_time, units = "hours"), 2),
               " hours has lapsed."))
  cat("i =", isetting, "/", nrow(SD), "\n")
  
  #print(SD[i, ])
  
  i <- result_list[[isetting]]$setting
  result <- result_list[[isetting]]$result
  
  ## gamma, b, m
  gamma <- SD$gamma[i]
  b <- SD$b[i]
  m <- SD$m[i]
  
  ## n, p_w, q_w
  n <- SD$n[i]
  p_w <- SD$p_w[i]
  q_w <- SD$q_w[i]
  p_star <- SD$p_star[i] # This is the degree of freedom of T test
  p <- 2 *p_w # this is the dimension of beta
  q <- q_w
  

  ##### test statistic #####
  test_stat_unadj <- sapply(result, function(l) l$test_stat_unadj)
  test_stat_adj <- sapply(result, function(l) l$test_stat_adj)
  
  ##### inference ####
  beta_hat_se_adj <- sapply(result, function(l) l$fit$beta_se_adj)
  
  # fit <- sapply(result, function(l) l$fit$beta_hat)
  # fit_mean <- colMeans(fit)
  
  cri_val <- (p_star * (n - q - 1)) / (n - p_star - q) *
    qf(1 - gamma, p_star, n - p_star - q)
  
  print(cri_val)
  

  if (truth_hypothesis == "H1") {
    power_unadj <- sum(test_stat_unadj > cri_val) / nsim
    power_adj <- sum(test_stat_adj > cri_val) / nsim
    power_vec <- c(power_unadj, power_adj)
    names(power_vec) <- c("power_unadj", "power_adj")
    print(power_vec)
  } else if (truth_hypothesis == "H0") {
    typeierror_unadj <- sum(test_stat_unadj > cri_val) / nsim
    typeierror_adj <- sum(test_stat_adj > cri_val) / nsim
    typeierror_vec <- c(typeierror_unadj,typeierror_adj )
    names(typeierror_vec) <- c("typeierror_unadj","typeierror_adj" )
    print(typeierror_vec)
  }
  
  # empirical standard error 
  mean_beta_hat_se_adj = rowMeans(beta_hat_se_adj)
  names(mean_beta_hat_se_adj) <- paste0("se_", names(mean_beta_hat_se_adj))
  
  result_df <- cbind(SD[i, ],
                     data.frame(power_unadj = power_unadj,
                                power_adj = power_adj,
                                t(mean_beta_hat_se_adj)))             
  
  result_df_collected <- rbind(result_df_collected, result_df)
  result_list_collected <- c(result_list_collected, list(list(
    result_df = result_df,
    test_stat_unadj = test_stat_unadj, 
    test_stat_adj = test_stat_adj
  )))
}
  saveRDS(result_df_collected, file = paste0("result_df_4_2acollected_nsim", nsim, ".RDS"))
  saveRDS(result_list_collected, file = paste0("result_list_4_2acollected_nsim", nsim, ".RDS"))
  write.csv(result_df_collected, file = paste0("result_df_4_2acollected_nsim", nsim, ".csv"))

```


```{r}

```



```{r}
# 3. Make plots and tables ------------------------------------------------
    nsim <- 500
    result <- readRDS("result_df_4_7acollected_nsim500.RDS")
    
    result$ASPNC_t_and_gt_shape_and_gt_t_theta <-
      paste0(result$ASPNC_t, result$gt_t_shape, result$gt_t_theta)
    result$gt_shape_and_gt_t_theta <-
      paste0(result$gt_t_shape, result$gt_t_theta)
    
    # added delta_ATE
    result$delta_ATE <- round(result$ATE2_t - result$ATE1_t, 1) 
    result$delta_ATE_factor <- as.factor(result$delta_ATE)
    levels(result$delta_ATE_factor) <- c("0.1"=TeX(r'($\Delta$ATE = 0.1)'),
                                     "0.2"=TeX(r'($\Delta$ATE = 0.2)'))
    result$ATE_t_and_ft_shape_ft_theta <- paste0(result$delta_ATE, " ", result$ft_t_theta, " ",result$ft_t_shape)
    
```


```{r}
result %>% 
    ggplot(aes(x = gamma2, y = power_adj, linetype = factor(gt_shape_and_gt_t_theta),
               color = factor(ASPNC_t))) +
    geom_line() +
    facet_grid(~delta_ATE_factor, labeller = label_parsed)+
    geom_hline(yintercept = 0.8, linetype = 2) +
    scale_linetype_discrete(guide = "none") +
    scale_color_discrete(guide = "none") +
    # scale_linetype_discrete(name = TeX(r'($g_t$ shape)'),
    #                         labels = c(TeX(r'(constant)'),
    #                                    TeX(r'(linear $\theta_g = -0.3$)'),
    #                                    TeX(r'(linear $\theta_g = 0$)'),
    #                                    TeX(r'(linear $\theta_g = 0.3$)'),
    #                                    TeX(r'(quadratic $\theta_g = -0.3$)'),
    #                                    TeX(r'(quadratic $\theta_g = 0$)'),
    #                                    TeX(r'(quadratic $\theta_g = 0.3$)')
    #                                    ))+
    # scale_color_discrete(name = TeX(r'(AEO)'),
    #                      labels = c(TeX(r'($AEO^* = AEO^w = 0.2$)'),
    #                                 TeX(r'($AEO^* = AEO^w = 0.4$)'),
    #                                 TeX(r'($AEO^* = AEO^w = 0.8$)'),
    #                                 TeX(r'($AEO^* = AEO^w = 1$)'),
    #                                 TeX(r'($AEO^* = AEO^w = 2$)'))) +
    # scale_color_discrete(name = TeX(r'($ATE^* = ATE^w$, $ASPN^* = ASPN^w$)'),
    #                      labels = c(TeX(r'($ATE = 1.2$, $ASPN = 0.2$)'),
    #                                 TeX(r'($ATE = 1.2$, $ASPN = 0.3$)'),
    #                                 TeX(r'($ATE = 1.2$, $ASPN = 0.4$)'),
    #                                 TeX(r'($ATE = 1.3$, $ASPN = 0.2$)'),
    #                                 TeX(r'($ATE = 1.3$, $ASPN = 0.3$)'),
    #                                 TeX(r'($ATE = 1.3$, $ASPN = 0.4$)'))) +
    xlab(TeX(r'($\theta_w^*$)')) +
    ylab("power") +
    #ggtitle(TeX(r'($EO^w(t)$: weekend effect)')) +
    coord_cartesian(ylim = c(0.5, 0.83), xlim = c(-1, 1)) +
    scale_y_continuous(breaks = seq(from = 0.1, to = 1, by = 0.1)) +
    scale_x_continuous(breaks = c(-1,0,1)) +
    # facet_grid(gt_t_theta ~ ASPNC_t, labeller = label_both) +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave(paste0("figure 4_7 - weekend power.pdf"), width = 8, height = 8) 
```

`
```{r}
se_beta1_w0 <- result %>% filter(delta_ATE == 0.2) %>% dplyr::select(se_beta1_w0)
th_se <- mean(se_beta1_w0$se_beta1_w0)

result %>% 
    filter(delta_ATE == 0.2) %>% 
    ggplot(aes(x = gamma2, y = se_Intercept...trt...1,
               linetype = factor(gt_shape_and_gt_t_theta),
               color = factor(ASPNC_t))) +
    geom_line()+
    #facet_grid(~ gt_t_shape, labeller = gt_t_shape_labeller)+
    geom_hline(yintercept = th_se, linetype = 2)+ 
    # scale_linetype_discrete(guide = "none") +
    # scale_color_discrete(guide = "none") +
    scale_linetype_discrete(name = TeX(r'($g_t$ shape)'),
                            labels = c(TeX(r'(constant)'),
                                       TeX(r'(linear $\theta_g = -0.3$)'),
                                       TeX(r'(linear $\theta_g = 0$)'),
                                       TeX(r'(linear $\theta_g = 0.3$)'),
                                       TeX(r'(quadratic $\theta_g = -0.3$)'),
                                       TeX(r'(quadratic $\theta_g = 0$)'),
                                       TeX(r'(quadratic $\theta_g = 0.3$)')
                                       ))+
    scale_color_discrete(name = TeX(r'(AEO)'),
                         labels = c(TeX(r'($AEO^* = AEO^w = 0.2$)'),
                                    TeX(r'($AEO^* = AEO^w = 0.4$)'),
                                    TeX(r'($AEO^* = AEO^w = 0.8$)'),
                                    TeX(r'($AEO^* = AEO^w = 1$)'),
                                    TeX(r'($AEO^* = AEO^w = 2$)'))) +
    xlab(TeX(r'($\theta_w^*$)')) +
    ylab(TeX(r'(sd($\hat{\beta})$)')) +
    #ggtitle(TeX(r'($\beta_1$ se)')) +
    coord_cartesian(ylim = c(0.065, 0.076), xlim = c(-1, 1)) +
    # scale_y_continuous(breaks = seq(from = 0.1, to = 1, by = 0.1)) +
    scale_x_continuous(breaks = c(-1,0,1)) +
    # facet_grid(gt_t_theta ~ ASPNC_t, labeller = label_both) +
    theme_bw() + 
    myggfont() +
    theme(legend.text.align = 0, plot.title = element_text(hjust = 0.5))
ggsave(paste0("figure 4_7 - weekend se.pdf"), width = 12, height = 9) 
  
```

