---
title: "DrinkLess Data Analysis"
author: "Jeremy Lin"
date: "2024-04-18"
output: 
  pdf_document :
    keep_tex: true
    extra_dependencies: "subfig"
header-includes:
 - \usepackage{booktabs}
 - \usepackage{longtable}
 - \usepackage{array}
 - \usepackage{multirow}
 - \usepackage{wrapfig}
 - \usepackage{float}
 - \usepackage{subfig}
 - \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nlme)
library(Matrix)
library(MASS)
library(rootSolve)
library(geepack)
library(lme4)
library(mvtnorm)
library(reshape2)
library(knitr)
library(ggplot2)
library(tidyr)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(kableExtra)
library(corrplot)
library(robustHD)
library(pracma)
library(xtable)
library(latex2exp)
library(janitor)
library(ggpubr)
library(lubridate)
# parallel computing libraries
library(foreach)
#library(doMC)
# beep beep 
library(beepr)
library(doParallel)
library(doSNOW)
library(utils)
library(foreach)
library(doRNG)
library(geepack)
```

```{r echo=FALSE}
#rm(list = ls())

knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, results = "hide", 
                      fig.pos = 'H', cache = FALSE, 
                      eval = TRUE)
# load functions
source("~/Documents/Research/causal_excursion_mult_trt/R code/functions_util.R")

# load data set 
dta <- readRDS("DrinkLess_data_primary_analysis.RDS")
```


```{r}
# EDA 
# there is no missing data in this dataset
summary(dta)

# n_sample = 349  participants (paper said 42 so 5 drop during the study?)
n_sample = length(unique(dta$ID))
id <- unique(dta$ID)

# create table for participant versus timepoints 
na_vec <- rep(NA, n_sample)
id_tbl <- data.frame(
  id = na_vec,
  n_timepoints = na_vec,
  max_time = na_vec ,
  time_complete = na_vec
)

for (i in 1:n_sample) {
  id_tbl$id[i] <- id[i]
  time_i <- dta[which(dta$ID == id[i]), "decision_index"]
  id_tbl$n_timepoints[i] <- dim(time_i)[1] 
  id_tbl$max_time[i] <- max(time_i$decision_index)
  id_tbl$time_complete[i] <- id_tbl$n_timepoints[i] == (id_tbl$max_time[i])
}

id_tbl

# all participants have full timpepoints
which(id_tbl$time_complete == FALSE)


```

```{r}
# data transformation
# create lag variable
dta$seconds_8to9.lag  <- c(0,head(dta$seconds_8to9,-1))

# attach availability column for estimator purposes (set I =1 for all time point)
dta$I <- 1

# add probability treatment (required in our estimator)
dta$prob_A <- sapply(dta$treatment_cate, function(l) ifelse(l == 0, 0.4, 
                                    ifelse(l == 1, 0.3, 0.3)) )

dta <- dta %>% mutate(AUDIT_hazardous = ifelse(AUDIT_score >= 8 & AUDIT_score <= 15, 1, 0))
dta <- dta %>% mutate(AUDIT_harmful = ifelse(AUDIT_score >= 16 & AUDIT_score <= 19, 1, 0))
dta <- dta %>% mutate(AUDIT_atRisk = ifelse(AUDIT_score >= 20 & AUDIT_score <= 40, 1, 0))

# make it as dataframe
dta <- as.data.frame(dta)

# # save data 
saveRDS(dta, "DrinkLess_processed.RDS")
# saveRDS(HeartSteps_data_primary_analysis, "HeartSteps_data_primary_analysis_modified.RDS")
# write_csv(HeartSteps_data_primary_analysis, "HeartSteps_data_primary_analysis_modified.csv")
```


```{r}
# # estimate availability
# # empirical estimate
# # max time point 
# time_max <- max(id_tbl$max_time)
# It_estimate <- rep(NA, time_max)
# for (i in 1:time_max) {
#   It_estimate[i] <- mean(dta[which(dta$decision.index.nogap.new == i), "I"])
# }
# # availability is roughly around 0.8 (after time 210 is fluctuating due to not that many individual have them)
# #It_estimate
# 
# #summary(dta)
dta <- readRDS("DrinkLess_processed.RDS")

var(dta$seconds_8to9)
sum(dta$seconds_8to9 == 0) / length(dta$seconds_8to9)

var_t <- rep(NA, 30)
for (t in 1:30) {
  var_t[t] <- dta %>% filter(decision_index == t) %>% dplyr::select(seconds_8to9) %>% unlist() %>%  var()
}

mean(var_t)

plot(x = 1:30, y = var_t)
1.56 /8517.41
```

# Analysis

```{r eval=FALSE}
# fitting our estimator 
id_varname = c("ID")
decision_time_varname = c("decision_index")
treatment_varname = c("treatment_cate")

avail_varname = c("I")
rand_prob_varname = "prob_A"
trt_level = 2

moderator_varname <- c()
outcome_varname = c("seconds_8to9")
control_varname <- c()

fit1 <- wcls_categorical_treatment(
  dta = dta,
  id_varname = id_varname,
  decision_time_varname = decision_time_varname,
  treatment_varname = treatment_varname,
  outcome_varname = outcome_varname,
  control_varname = control_varname,
  moderator_varname = moderator_varname,
  rand_prob_varname = rand_prob_varname,
  avail_varname = avail_varname,
  trt_level = trt_level,
  estimator_initial_value = NULL
)
```



```{r}
# fitting our estimator 
id_varname = c("ID")
decision_time_varname = c("decision_index")
treatment_varname = c("treatment_cate")

avail_varname = c("I")
rand_prob_varname = "prob_A"
trt_level = 2

moderator_varname <- c()
outcome_varname = c("seconds_8to9")
control_varname <- c("age", "AUDIT_score", "gender","decision_index", "seconds_8to9.lag")

fit1a <- wcls_categorical_treatment(
  dta = dta,
  id_varname = id_varname,
  decision_time_varname = decision_time_varname,
  treatment_varname = treatment_varname,
  outcome_varname = outcome_varname,
  control_varname = control_varname,
  moderator_varname = moderator_varname,
  rand_prob_varname = rand_prob_varname,
  avail_varname = avail_varname,
  trt_level = trt_level,
  estimator_initial_value = NULL
)


#fit1a$conf_int_adjusted_t

# fit 1 b use time as moderator
moderator_varname = c("decision_index")

fit1b <- wcls_categorical_treatment(
  dta = dta,
  id_varname = id_varname,
  decision_time_varname = decision_time_varname,
  treatment_varname = treatment_varname,
  outcome_varname = outcome_varname,
  control_varname = control_varname,
  moderator_varname = moderator_varname,
  rand_prob_varname = rand_prob_varname,
  avail_varname = avail_varname,
  trt_level = trt_level,
  estimator_initial_value = NULL
)

#fit1b$conf_int_adjusted_t

# fit 1c use location as moderator 
moderator_varname = c("AUDIT_score")

fit1c <- wcls_categorical_treatment(
  dta = dta,
  id_varname = id_varname,
  decision_time_varname = decision_time_varname,
  treatment_varname = treatment_varname,
  outcome_varname = outcome_varname,
  control_varname = control_varname,
  moderator_varname = moderator_varname,
  rand_prob_varname = rand_prob_varname,
  avail_varname = avail_varname,
  trt_level = trt_level,
  estimator_initial_value = NULL
)

#fit1c$conf_int_adjusted_t

# model when using Audit as factor (using hazardous as baseline)
moderator_varname = c("AUDIT_harmful","AUDIT_atRisk")
control_varname <- c("age", "AUDIT_harmful","AUDIT_atRisk","gender","decision_index", "seconds_8to9.lag")

fit1d <- wcls_categorical_treatment(
  dta = dta,
  id_varname = id_varname,
  decision_time_varname = decision_time_varname,
  treatment_varname = treatment_varname,
  outcome_varname = outcome_varname,
  control_varname = control_varname,
  moderator_varname = moderator_varname,
  rand_prob_varname = rand_prob_varname,
  avail_varname = avail_varname,
  trt_level = trt_level,
  estimator_initial_value = NULL
)


```

```{r}
fit_1a_summary <- wcls_summary(fit1a)
fit_1b_summary <- wcls_summary(fit1b)
fit_1c_summary <- wcls_summary(fit1c)
fit_1d_summary <- wcls_summary(fit1d)
```


```{r}
res1a <- data.frame(Estimate =fit1a$beta_hat,
           Sd = fit1a$beta_se)
res1a <- cbind(res1a, fit1a$conf_int_adjusted_t, p_val = fit_1a_summary$`Pr(>|t|)`)

res1b <- data.frame(Estimate =fit1b$beta_hat,
           Sd = fit1b$beta_se)
res1b <- cbind(res1b, fit1b$conf_int_adjusted_t, p_val = fit_1b_summary$`Pr(>|t|)`)

res1c <- data.frame(Estimate =fit1c$beta_hat,
           Sd = fit1c$beta_se)
res1c <- cbind(res1c, fit1c$conf_int_adjusted_t, p_val = fit_1c_summary$`Pr(>|t|)`)

res1d <- data.frame(Estimate =fit1d$beta_hat,
           Sd = fit1d$beta_se )
res1d <- cbind(res1d, fit1d$conf_int_adjusted_t, p_val = fit_1d_summary$`Pr(>|t|)`)
```

```{r resdif1a}
# # between treatment marginal
L1a <- matrix(c(1, -1), nrow = 1)
diff1a <- wcls_glh(fit1a, L1a)

resdiff1a <- cbind(name = c("beta1 - beta2"),
                   estimator = diff1a$summary$Estimate, 
                   sd = diff1a$summary$`Std. Error`, 
                   diff1a$conf_int, 
                   pval = diff1a$summary$`Pr(>|t|)`)
```

```{r resdif1b}
L1b <- matrix(c(1, 0, -1, 0, 0, 1, 0, -1), ncol = 4, byrow = TRUE)
diff1b <- wcls_glh(fit1b, L1b)

resdiff1b <- cbind(name = c("beta1- beta3", "beta2 - beta4"),
                   estimator = diff1b$summary$Estimate, 
                   sd = diff1b$summary$`Std. Error`, 
                   diff1b$conf_int, 
                   pval = diff1b$summary$`Pr(>|t|)`)
# simultaneous p value
resdiff1b <- rbind(resdiff1b, c("simultaneous", 0, 0, 0, 0, diff1b$simultaneous_test))
```

```{r resdif1d1}
L1d1 <- matrix(c(1, 1, 0, 0, 0, 0), ncol = 6, byrow = TRUE)

diff1d1 <- wcls_glh(fit1d, L1d1)
resdiff1d1 <- cbind(name = c("beta1 +beta2"),
                    estimator = diff1d1$summary$Estimate, 
                   sd = diff1d1$summary$`Std. Error`, 
                   diff1d1$conf_int, 
                   pval = diff1d1$summary$`Pr(>|t|)`)
```

```{r resdif1d2}
L1d2 <- matrix(c(1, 0, 1, 0, 0, 0), ncol = 6, byrow = TRUE)
diff1d2 <- wcls_glh(fit1d, L1d2)

resdiff1d2 <- cbind(name = c("beta1 + beta3"), 
                  estimator = diff1d2$summary$Estimate, 
                   sd = diff1d2$summary$`Std. Error`, 
                   diff1d2$conf_int, 
                   pval = diff1d2$summary$`Pr(>|t|)`)
```

```{r resdif1d3}
L1d3 <- matrix(c(0, 0, 0, 1, 1, 0), ncol = 6, byrow = TRUE)

diff1d3 <- wcls_glh(fit1d, L1d3)

resdiff1d3 <- cbind(name =c("beta4 + beta5"),
                    estimator = diff1d3$summary$Estimate, 
                   sd = diff1d3$summary$`Std. Error`, 
                   diff1d3$conf_int, 
                   pval = diff1d3$summary$`Pr(>|t|)`)
```

```{r resdif1d4}
L1d4 <- matrix(c(0, 0, 0, 1, 0, 1), ncol = 6, byrow = TRUE)

diff1d4 <- wcls_glh(fit1d, L1d4)

resdiff1d4 <- cbind(name = c("beta4 + beta6"),
                    estimator = diff1d4$summary$Estimate, 
                   sd = diff1d4$summary$`Std. Error`, 
                   diff1d4$conf_int, 
                   pval = diff1d4$summary$`Pr(>|t|)`)
```

```{r resdif1d5}
L1d5 <- matrix(c(-1, 0, 0, 1, 0, 0), ncol = 6, byrow = TRUE)

diff1d5 <- wcls_glh(fit1d, L1d5)

resdiff1d5 <- cbind(name = c("beta4 - beta1"), 
                    estimator = diff1d5$summary$Estimate, 
                   sd = diff1d5$summary$`Std. Error`, 
                   diff1d5$conf_int, 
                   pval = diff1d5$summary$`Pr(>|t|)`)
```

```{r resdif1d6a}
L1d6a <- matrix(c(-1, -1, 0, 1, 1, 0), ncol = 6, byrow = TRUE)

diff1d6a <- wcls_glh(fit1d, L1d6a)

resdiff1d6a <- cbind(name = c("beta4 +beta5  - beta1 - beta2"), 
                    estimator = diff1d6a$summary$Estimate, 
                   sd = diff1d6a$summary$`Std. Error`, 
                   diff1d6a$conf_int, 
                   pval = diff1d6a$summary$`Pr(>|t|)`)
```

```{r resdif1d6}
L1d6 <- matrix(c(-1, 0, 0, 1, 0, 0,
                 0, -1, 0, 0, 1, 0), ncol = 6, byrow = TRUE)

diff1d6 <- wcls_glh(fit1d, L1d6)

#simultaneous pvalue
resdiff1d6 <-  c("simultaneous", 0, 0, 0, 0, diff1d6$simultaneous_test)
```

```{r resdif1d7a}
L1d7a <- matrix(c(-1, 0, -1, 1, 0, 1), ncol = 6, byrow = TRUE)

diff1d7a <- wcls_glh(fit1d, L1d7a)

resdiff1d7a <- cbind(name = c("beta4 + beta6 - beta1 - beta3"), 
                    estimator = diff1d7a$summary$Estimate, 
                   sd = diff1d7a$summary$`Std. Error`, 
                   diff1d7a$conf_int, 
                   pval = diff1d7a$summary$`Pr(>|t|)`)
```

```{r resdif1d7}
L1d7 <- matrix(c(-1, 0, 0, 1, 0, 0,
                 0, 0, -1, 0, 0, 1), ncol = 6, byrow = TRUE)

diff1d7 <- wcls_glh(fit1d, L1d7)


#simultaneous pvalue
resdiff1d7 <- c("simultaneous", 0, 0, 0, 0, diff1d7$simultaneous_test)
```

```{r res dif1d }
resdiff1d <- rbind (resdiff1d1, 
                 resdiff1d2,
                 resdiff1d3,
                 resdiff1d4,
                 resdiff1d5,
                 resdiff1d6a,
                 resdiff1d6,
                 resdiff1d7a,
                 resdiff1d7
                 )
```


## Marginal Model 

\begin{align}
    Y_t = \beta_1 (Intercept : trt = 1) + \beta_2 (Intercept : trt = 2) + g_t^T\alpha + \epsilon_t
\end{align}

### Treatment Effect 

```{r results='asis'}
print(
kable(
  res1a,
  caption = "Intercept model no moderator",
  digits = 3
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "t adjusted" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_1a.tex")
)
```

Averaging over study days, delivering a standard message increases the average time of user using the app by 10.5 second ($95\%$ CI unadjusted = `r round(fit1a$conf_int[1,],2)`, $95\%$ CI z adjusted = `r round(fit1a$conf_int_adjusted_z[1,],2)`, $95\%$ CI t adjusted = `r round(fit1a$conf_int_adjusted_t[1,],2)`). 

Similarly, delivering new notification increasestime of user using the app by 12.1 second on average compared to user that received no notification ($95\%$ CI unadjusted = `r round(fit1a$conf_int[2,],2)`, $95\%$ CI z adjusted = `r round(fit1a$conf_int_adjusted_z[2,],2)`, $95\%$ CI t adjusted = `r round(fit1a$conf_int_adjusted_t[2,],2)`).


### Between Treatment effect

Averaging over study days, The effect between delivering walking suggestion versus antisedentary suggestions is not significant. 

```{r results='asis'}
print(
kable(
  resdiff1a,
  caption = "Intercept model no moderator",
  digits = 2
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "CI" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_resdif1a.tex")
)
```


## Decision point as moderator.  

\begin{align}
      Y_t = &\beta_1 (Intercept : trt = 1) + \beta_2 (time :trt = 1) + \\
            &\beta_3 (Intercept : trt = 2) + \beta_4 (time :trt = 2) + g_t^T\alpha + \epsilon_t
\end{align}

### Treatment effect

```{r results='asis'}
print(
kable(
  res1b,
  caption = "decision point as moderator",
  digits = 3
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "t adjusted" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_1b.tex")
)
```


Delivering a standard notification initially increases the time of participant using the app by 21.73 seconds on average compared to participant who did not receive any notification($95\%$ CI unadjusted = `r round(fit1b$conf_int[1,],2)`, $95\%$ CI z adjusted = `r round(fit1b$conf_int_adjusted_z[1,],2)`, $95\%$ CI t adjusted = `r round(fit1b$conf_int_adjusted_t[1,],2)`). The initial  effect decreases linearly  with time at 0.7 a day ($95\%$ CI unadjusted = `r round(fit1b$conf_int[2,],2)`, $95\%$ CI z adjusted = `r round(fit1b$conf_int_adjusted_z[2,],2)`, $95\%$ CI t adjusted = `r round(fit1b$conf_int_adjusted_t[2,],2)`). 

Delivering a new notification initially increases the time of participant using the app by 29.5 seconds on average compared to participant who did not receive any notification($95\%$ CI unadjusted = `r round(fit1b$conf_int[3,],2)`, $95\%$ CI z adjusted = `r round(fit1b$conf_int_adjusted_z[3,],2)`, $95\%$ CI t adjusted = `r round(fit1b$conf_int_adjusted_t[3,],2)`). The initial  effect decreases linearly  with time at 0.7 a day ($95\%$ CI unadjusted = `r round(fit1b$conf_int[4,],2)`, $95\%$ CI z adjusted = `r round(fit1b$conf_int_adjusted_z[4,],2)`, $95\%$ CI t adjusted = `r round(fit1b$conf_int_adjusted_t[4,],2)`). 

### Between treatment effect

```{r results='asis'}
print(
kable(
  resdiff1b,
  caption = "time moderator",
  digits = 4
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "CI" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_resdic1b.tex")
)
```

## Audit score as moderator

\begin{align}
      Y_t = &\beta_1 (Intercept : trt = 1) + \beta_2 (Audit score :trt = 1) + \\
            &\beta_3 (Intercept : trt = 2) + \beta_4 (Audit score :trt = 2) + g_t^T\alpha + \epsilon_t
\end{align}

### Treatment Effect

```{r results='asis'}
print(
kable(
  res1c,
  caption = "Audit Score as moderator",
  digits = 3
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "t adjusted" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_1c.tex")
) 
```

Neither new notification nor the new notification was significant. 

### Between treatment effect

## Audit Stratified (hazardous vs harmful vs at risk) as moderator 

\begin{align}
    Y_t = &\beta_1 (Intercept : trt = 1) + \beta_2 (audit harmful : trt = 1) + \beta_3 (audit at risk : trt = 1)\\
      &\beta_4 (Intercept : trt = 2) + \beta_5 (audit harmful : trt = 1) + \beta_6 (audit at risk : trt = 1) + g_t^T\alpha + \epsilon_t
\end{align}


### Treatment effect

```{r results='asis'}
print(
kable(
  res1d,
  caption = "Audit Score as moderator",
  digits = 3
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "t adjusted" = 2,
    " " = 1
  ))%>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_1d.tex")
)
```


Neither new notification nor the new notification was significant. 

### Between treatment effect

```{r results='asis'}
print(
kable(
  resdiff1d,
  caption = "big big table",
  digits = 3, 
  float = TRUE
) %>%
  add_header_above(c(
    " " = 1,
    "Effect" = 2,
    "CI" = 2,
    " " = 1
  )) %>% kable_styling(latex_options = "hold_position") %>% save_kable("table_DrinkLess_res1d.tex")
)
```



